Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-07-08 article.tex
Add discussion of uncertainty relative to device spec

The syringe pump system (EW-74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}. The syringe pump was programmed to run a predefined flow profile, using the 14.5 mm inner diameter of the syringe to ensure a correct flow rate. It should be noted that a 3 mL syringe was also evaluated, however its performance was significantly worse than the 10 mL syringe and regularly failed to resolve the desired flow profiles.

The pressure-regulated flow system used a pressure controller (MFCS-EZ, Fluigent, Inc.) connected to a house air line regulated at 500 mbar, as shown in Fig.~\ref{fig:system_lsci}c. This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution. Prior to running a flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure. The MAESFLO control software used feedback from the inline flow sensor to regulate the air pressure to achieve the desired flow rate.

@@

Table~\ref{tab:uncertainty_standard} shows a comparison of the standard uncertainties for repeatability ($u_\textnormal{repeat}$), reproducibility ($u_\textnormal{reproduce}$), and bias ($u_\textnormal{bias}$) for each system at the flow speeds tested in the 3-step experiments. These results quantify the observations from Fig.~\ref{fig:SvP-FS} that the pressure-regulated flow system is more stable, repeatable, and accurate at all the tested flow speeds. The combined and expanded uncertainties for both systems are presented in Table~\ref{tab:uncertainty_combined}. These results provide evidence of the superiority of the pressure-regulated flow system, particularly when attempting to produce small flow changes. With the syringe pump system, it would be impossible to reliably separate 20\% changes in relative flow from flow system noise at the 2.4 mm/s flow speed. This magnitude of uncertainty in flow generation would make it difficult to assess an optical system's ability to detect small changes in flow. This limitation is visually represented in Fig.~\ref{fig:SvP-FS}b, where the syringe pump fails to resolve the finer 0.2 mm/s flow changes. Using the pressure-regulated flow system, experiments could be designed with relative flow changes of only 1.5\% while remaining confident that the resulting optical system measurements were not caused by flow system noise. This level of certainty would also permit assessing improvements to optical system performance at this scale.

@@

The flow measurement performance assessment using the pressure-regulated flow system is shown in Fig.~\ref{fig:flow_mesi_lsci}. The relative flow measured by MESI and LSCI using the system described in Section \ref{sect:methods_mesi_system} are plotted alongside the flow sensor measurements from a single trial in Fig.~\ref{fig:flow_mesi_lsci}a. All relative flows were calculated using the average of the first flow step (1 mm/s) as the baseline. Data for each flow step were pooled and averaged across all four trials to assess the overall performance as seen in Fig.~\ref{fig:flow_mesi_lsci}b. The coefficients of determination ($R^2$) for this averaged MESI and LSCI data relative to the flow sensor were 0.988 and 0.839, respectively. The concordance correlation coefficients ($\rho_c$), a metric designed to evaluate reproducibility \cite{Lin.1989}, were 0.994 and 0.908, respectively. These results demonstrate both strong agreement between MESI and the flow sensor measurements and that MESI outperforms LSCI across large changes in relative flow. \textcolor{red}{Address apparent differences in performance for LSCI between Figs. \ref{fig:SvP-FS_LSCI}b and \ref{fig:flow_mesi_lsci}? The flow at the 5 mm/s step is $\sim$1.93$\times$ the flow at the 2.5 mm/s step in Fig. \ref{fig:flow_mesi_lsci}. Not quite the near-perfect agreement we see in Fig. \ref{fig:SvP-FS_LSCI}b.}

@@

Almost all microfluidic studies used for characterizing LSCI and MESI systems have been performed using syringe pumps. This study corroborates previous work \cite{Li:2014ca,Zhou:2011ey,Zeng.2020} that has shown syringe pumps do not produce stable flow outputs and demonstrates that single-exposure LSCI is sensitive enough to detect the resulting flow anomalies (Fig. \ref{fig:SvP-FS_LSCI}). Furthermore, the close agreement between the LSCI and flow sensor demonstrates that these flow anomalies could be incorrectly interpreted as noise in the optical imaging system when they are actual flow variations. Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials. Because microfluidic studies are commonly used to assess LSCI and MESI instrument performance, an unstable flow control system contributes additional noise to the measurements, making it more difficult to properly characterize a system. For example, the flow profiles in Fig. \ref{fig:SvP-FS} and the uncertainty analysis in Table \ref{tab:uncertainty_combined} show large errors and high variability within and across trials using the syringe pump. These instabilities in flow were caused entirely by the syringe pump, as independently validated using single-exposure LSCI in Fig. \ref{fig:SvP-FS_LSCI}a. Such instability would increase the uncertainty in the true performance of any instrument being evaluated. The same analysis shows that a more reliable flow controller, such as the pressure-regulated flow system, produces minimal error and much improved reproducibility, therefore facilitating a more robust instrument assessment.

\textcolor{red}{Discuss uncertainty analysis in more detail \textbf{Do we even need this section?} Compare results to manufacturer's spec. How to explain the syringe pump results being so far off? Accuracy +/- 0.5\%, Reproducibility +/- 0.05\%. The accuracy ($u_{bias}$) of the syringe pump is the primary source of uncertainty. Possibly move part of results text here instead?}

The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp}. The MESI estimates of relative flow outperformed LSCI at all flow speeds and closely followed the flow sensor measurements. This included the periods with no flow at the beginning and end of each experiment, where LSCI still measured relative flow of almost 0.5$\times$ the baseline. As seen in Fig. \ref{fig:error}, the \textit{largest} absolute error for MESI was comparable to that of the \textit{smallest} absolute error for LSCI. \textcolor{red}{Compare to previous measurements by Shams? Can we suggest that the reduced error was caused by the syringe pump?} While MESI exhibited slightly more variability during individual flow profile steps (Fig. \ref{fig:flow_mesi_lsci}a), this was probably introduced by the fitting process required to calculate $\tau_c$. This nonlinear fitting was also likely responsible for the increased error seen with MESI for flow speeds between 3.5 to 6 mm/s. \textcolor{red}{Can we actually claim this? If yes, then what exactly is happening? Is it just numerical changes in the fitting caused by increases in $\rho$?} It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located. Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.

>>>>

The syringe pump system (74905-04, Cole Parmer Instrument Company, LLC.) was connected to the flow sensor (Fig.~\ref{fig:system_lsci}b) and a 10 mL plastic syringe (\#302149, BD) was filled with the blood-mimicking solution described in Section \ref{sect:methods_phantom}. The syringe pump was programmed to run a predefined flow profile, using the 14.5 mm inner diameter of the syringe to ensure a correct flow rate. It should be noted that a 3 mL syringe was also evaluated, however its performance was worse than the 10 mL syringe and could not hold sufficient volume for all trials without being refilled.

The pressure-regulated flow system used a pressure controller (MFCS-EZ with 69 mbar channel, Fluigent, Inc.) connected to a house air line regulated at 500 mbar, as shown in Fig.~\ref{fig:system_lsci}c. This controller outputted regulated air flow (up to 69 mbar) to a 15 mL pressurized reservoir (Fluiwell-1C, Fluigent, Inc.) filled with the blood-mimicking solution. Prior to running a flow program, a calibration was performed that accounted for the resistance from the tubing, microfluidic channel, and hydrostatic pressure. The MAESFLO control software used feedback from the inline flow sensor to regulate the air pressure to achieve the desired flow rate.

@@

Table~\ref{tab:uncertainty_standard} shows a comparison of the standard uncertainties for repeatability ($u_\textnormal{repeat}$), reproducibility ($u_\textnormal{reproduce}$), and bias ($u_\textnormal{bias}$) for each system at the flow speeds tested in the 3-step experiments. These results quantify the observations from Fig.~\ref{fig:SvP-FS} that the pressure-regulated flow system is more stable, repeatable, and accurate at all the tested flow speeds. The combined and expanded uncertainties for both systems are presented in Table~\ref{tab:uncertainty_combined}. These results provide evidence of the superiority of the pressure-regulated flow system, particularly when attempting to produce small flow changes. With the syringe pump system, it would be impossible to reliably separate 20\% changes in relative flow from flow system noise at the 2.4 mm/s flow speed. This magnitude of uncertainty in flow generation would make it difficult to assess an optical system's ability to detect small changes in flow. This limitation is visually represented in Fig.~\ref{fig:SvP-FS}b, where the syringe pump fails to resolve the finer 0.2 mm/s flow changes. Using the pressure-regulated flow system, experiments could be designed with relative flow changes of only 1.25\% while remaining confident that the resulting optical system measurements were not caused by flow system noise. This level of certainty would also permit assessing improvements to optical system performance at this scale.

@@

The flow measurement performance assessment using the pressure-regulated flow system is shown in Fig.~\ref{fig:flow_mesi_lsci}. The relative flow measured by MESI and LSCI using the system described in Section \ref{sect:methods_mesi_system} are plotted alongside the flow sensor measurements from a single trial in Fig.~\ref{fig:flow_mesi_lsci}a. All relative flows were calculated using the average of the first flow step (1 mm/s) as the baseline. Data for each flow step were pooled and averaged across all four trials to assess the overall performance as seen in Fig.~\ref{fig:flow_mesi_lsci}b. The coefficients of determination ($R^2$) for this averaged MESI and LSCI data relative to the flow sensor were 0.988 and 0.839, respectively. The concordance correlation coefficients ($\rho_c$), a metric designed to evaluate reproducibility \cite{Lin.1989}, were 0.994 and 0.908, respectively. These results demonstrate both strong agreement between MESI and the flow sensor measurements and that MESI outperforms LSCI across large changes in relative flow. It should be noted that the apparent disparity in LSCI performance between Figs. \ref{fig:SvP-FS_LSCI}b and \ref{fig:flow_mesi_lsci} is primarily the result of different flow steps being used as the baseline in each set of experiments. While not an exact comparison, the LSCI measured flow at the 5 mm/s step is 1.94$\times$ the flow at the 2.5 mm/s step in Fig. \ref{fig:flow_mesi_lsci}, approximately mirroring the 2$\times$ change seen between the 2.4 and 4.8 mm/s steps in Fig. \ref{fig:SvP-FS_LSCI}b.

@@

Almost all microfluidic studies used for characterizing LSCI and MESI systems have been performed using syringe pumps. This study corroborates previous work \cite{Li:2014ca,Zhou:2011ey,Zeng.2020} that has shown syringe pumps do not produce stable flow outputs and demonstrates that single-exposure LSCI is sensitive enough to detect the resulting flow anomalies (Fig. \ref{fig:SvP-FS_LSCI}). Furthermore, the close agreement between LSCI and the flow sensor demonstrates that these anomalies could be incorrectly interpreted as noise in the optical imaging system when they are actual flow variations. Compared to the syringe pump, the pressure-regulated flow system produced much more stable and reproducible flow outputs across all trials. Because microfluidic studies are commonly used to assess LSCI and MESI instrument performance, an unstable flow control system contributes additional noise to the measurements, making it more difficult to properly characterize a system. For example, the flow profiles in Fig. \ref{fig:SvP-FS} and the uncertainty analysis in Table \ref{tab:uncertainty_combined} show large errors and high variability within and across trials using the syringe pump. These instabilities in flow were caused entirely by the syringe pump, as independently validated using single-exposure LSCI in Fig. \ref{fig:SvP-FS_LSCI}a. Such instability would increase the uncertainty in the true performance of any instrument being evaluated. The same analysis shows that a more reliable flow controller, such as the pressure-regulated flow system, produces minimal error and much improved reproducibility, therefore facilitating a more robust instrument assessment.

The measured noise levels quantified by $u_\textnormal{repeat}$ follow the specifications published by the manufacturers of both flow control systems. This indicates that the stability results shown are typical and representative of actual performance differences. The $u_\textnormal{repeat}$ for the syringe pump across all flow steps (up to 1.86\%) was within the manufacturer's tolerances, which stated that instantaneous flow should be $\pm$2\% from the mean value. The $u_\textnormal{repeat}$ for the pressure-regulated flow system (up to 0.55\%) slightly exceeded the manufacturer's specifications, which indicated that the best stability achievable with this system configuration was $\pm$0.5\% from the mean value. Much larger differences arose from issues with reproducibility and accuracy, with the $u_\textnormal{reproduce}$ and $u_\textnormal{bias}$ of the syringe pump measuring several orders of magnitude higher than those of the pressure-regulated flow system. The syringe pump greatly exceeded the manufacturer's tolerances for both reproducibility ($\pm$0.05\%) and accuracy ($\pm$0.5\%). Corresponding specifications were not available for the pressure-regulated flow system. While it is possible that using a glass syringe \cite{Zhou:2011ey} or sending the device for manufacturer recalibration could improve performance on the syringe pump, it is unlikely to achieve the stability and reliability seen with the pressure-regulated flow system.

The evaluation of MESI and single-exposure LSCI using the pressure-regulated flow system further demonstrates the superiority of the MESI technique \cite{Kazmi:2013hp}. The MESI estimates of relative flow outperformed LSCI at all flow speeds and closely followed the flow sensor measurements. This included the periods with no flow at the beginning and end of each experiment, where LSCI still measured relative flow of almost 0.5$\times$ the baseline. As seen in Fig. \ref{fig:error}, the \textit{largest} absolute error for MESI was comparable to that of the \textit{smallest} absolute error for LSCI. While MESI exhibited slightly more variability during individual flow profile steps (Fig. \ref{fig:flow_mesi_lsci}a), this was likely caused by the fitting process required to calculate $\tau_c$. Numerical artifacts introduced by this nonlinear fitting could also be responsible for the increased error seen with MESI at flow speeds between 3.5 to 6 mm/s. It is also possible that discrepancies between MESI and the flow sensor could be attributed to a difference in flow between the microfluidic channel and the inlet line where the flow sensor is located. Such a difference could be caused by air leakage in the inlet or outlet port of the phantom, which would reduce the flow measured by the MESI system without impacting the upstream flow measured by the flow sensor.
